### 2014-05-21 remy_eval.tex
Fixes to Remy section

We also used Remy to assess how performance varies based on the
specificity of the assumptions used at design time, by building
one RemyCC for a link speed known exactly \emph{a priori}, and
one that assumes only that the link speed will lie within a tenfold range:

@@

@@

\item {\bf Cellular wireless:} We measured the downlink capacity of the
  Verizon and AT\&T LTE cellular services while mobile, by carefully
  saturating the downlink (without causing buffer overflow) and
  recording when packets made it to the user device. We recreate this
  link within ns-2, queueing packets until they are released to the
  receiver at the same time they were released in the trace. This
  setup probes the RemyCC's resilience to ``model mismatch'' --- in
  both the Verizon and AT\&T traces, throughput and round-trip time
  were outside the limits of the RemyCC design range.

>>>>

\begin{comment}
We also used Remy to assess how performance varies based on the
specificity of the assumptions used at design time, by building
one RemyCC for a link speed known exactly \emph{a priori}, and
one that assumes only that the link speed will lie within a tenfold range:

@@

\vspace{\baselineskip}
\end{comment}

@@

\item {\bf Cellular wireless:} We used the Saturator traces (Section~\ref{ss:saturator}) of the
  Verizon and AT\&T LTE cellular services. We recreated these
  links within ns-2, queueing packets until they are released to the
  receiver at the same time they were released in the trace. This
  setup partly probes the RemyCC's resilience to ``model mismatch'' --- in
  both the Verizon and AT\&T traces, throughput and round-trip time
  strayed outside the limits of the RemyCC design range.
